---
title: "Advanced Feature Selection"
output: html_document
---

### Scope

The scope of this notebook is to provide instructions on how to do advanced feature selection using all of the models created during a DataRobot autopilot.

### Background

This is the procedure we are going to follow:

* Calculate the feature importance for each trained model
* Get the feature ranking for each trained model
* Get the ranking distribution for each feature across models
* Sort by mean rank and visualize

### Requirements

- R version 3.6.2
-  DataRobot API version 2.16.0. 
Small adjustments might be needed depending on the R version and DataRobot API version you are using.

Full documentation of the R package can be found here: https://cran.r-project.org/web/packages/datarobot/index.html

It is assumed you already have a DataRobot <code>Project</code> object and a DataRobot <code>Model </code> object.

#### Import Packages
```{r results = 'hide', warning=FALSE, message=FALSE}
library(datarobot)
library(dplyr)
library(stringr)
library(ggplot2)
library(purrr)
```

I do not want to pick all of the models. I will ignore Blender, Auto-Tuned, and models trained with a small percentage of data. Lastly, I only care about models that were trained on 'Informative Features' but this can change depending on your needs.

```{r echo=FALSE, results = 'hide', warning=FALSE, message=FALSE}
#This piece of code will not show
ConnectToDataRobot(endpoint = "YOUR_DATAROBOT_HOSTNAME", 
                   token = "YOUR_API_KEY")

project <- GetProject("YOUR_PROJECT_ID")
allModels <- ListModels(project)
modelFrame <- as.data.frame(allModels)
metric <- modelFrame$validationMetric
if (project$metric %in% c('AUC', 'Gini Norm')) {
  bestIndex <- which.max(metric)
} else {
  bestIndex <- which.min(metric)
}
model <- allModels[[bestIndex]]
model$modelType
```

```{r}
models <- ListModels(project)
bestmodels <- Filter(function(m) m$featurelistName == "Informative Features" & m$samplePct >= 64 &  m$samplePct <= 80 & !str_detect(m$modelType, 'Blender') & !str_detect(m$modelType, 'Auto-Tuned') , models)
bestmodels <- Filter(function(m) m$samplePct >= 63, models)
```

Then, we will Collect all the feature impact info.

```{r}
all_impact<- NULL
for(i in 1:length(bestmodels)) {  
    featureImpact <- GetFeatureImpact(bestmodels[[i]])
    featureImpact$modelname <- bestmodels[[i]]$modelType
    all_impact <- rbind(all_impact,featureImpact)
  }
```

Now we can plot these features

```{r}
all_impact <- all_impact %>% mutate(finalnorm = impactUnnormalized/max(impactUnnormalized))
p <- ggplot(all_impact, aes(x=reorder(featureName, -finalnorm, FUN=median), y=finalnorm))
p + geom_boxplot() + coord_flip()
```

Finally, create a new feature list with the top features and re-run DataRobot's Autopilot

```{r eval=FALSE}
## Process Feature impact
ranked_impact <- all_impact %>% group_by(featureName) %>% 
    summarise(impact = mean(finalnorm)) %>% 
    arrange(desc(impact))

#New Feature List
topfeatures <- pull(ranked_impact,featureName)
No_of_features_to_select <- 4
listname = paste0("TopFI_", No_of_features_to_select)
Feature_id_percent_rank = CreateFeaturelist(projectid, listName= listname , featureNames = topfeatures[1:No_of_features_to_select])$featurelistId

# Run AutoPilot on new Top Features
StartNewAutoPilot(projectid,featurelistId = Feature_id_percent_rank)
WaitForAutopilot(projectid)
```